---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sds

<!-- badges: start -->
[![R-CMD-check](https://github.com/hypertidy/spatial.datasources/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/hypertidy/spatial.datasources/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of sds is to provide spatial data sources!!

## Installation

You can install the development version of sds from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hypertidy/sds")
```

## Example

This shows some of the variety of the sources available. 

```{r example}
library(sds)

gebco() ## a global seamless topography (bathymetry and elevation)

CGAZ()  ## a global nations boundaries dataset

CGAZ_sql(c("New Zealand", "Australia")) ## a SQL query for the CGAZ polygons

cop30()  ## a global 30m elevation data set 


mpc()  ## return STAC collections for use with GDAL

mpc( datetime = as.Date(c("2019-06-01", "2019-08-01")), 
    bbox = c(-148.56, -147.44, 60.80, 61.18), asset = "visual")

## or return just the string a for jsonlite read
js <- jsonlite::fromJSON(mpc(stacit  = F))
## do it how you like
js$features$assets$visual$href


```


There are image tile servers: 

```{r tiles}
wms_arcgis_mapserver_ESRI.WorldImagery_tms()
wms_openstreetmap_tms()

## not shown else will reveal my INSTANCE_ID
wms <- sentinel2_wms()
```

And a very specific sea ice source: 

```{r nsidc}
nsidc_seaice(hemisphere = "south")
nsidc_seaice(hemisphere = "north")
```


## Code of Conduct
  
Please note that the sds project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
